---
title: "HW 01 - data science hw"
author: "esubalew vande hey"
date: "2023-01-12"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
```

### First Data visualization homework (exercises 3.2)

the graph shows a negative correlation between engine size and efficiency. in Lamens; the larger the engine the lower the efficiency of a car.


```{r first mileage graph}
 ggplot(data = mpg) + 
 geom_point(mapping = aes(x = displ, y = hwy, colour = "blue")) 
```

the colour isnt blue because the command colour = "blue" was placed inside of the aesthetic mapping
```{r first mileage graph}
 ggplot(data = mpg) + 
 geom_point(mapping = aes(x = displ, y = hwy), colour = "blue")  
```


```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = drv, y = cyl))
```

3.5.1: 
1. what happens when you when you facet on a continuous variable?
the continuous variable will become a catagorical variable. one column or row for each value/variable.

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(drv ~ cyl)
```

2. what do the empty cells above mean? how do they relate to this plot?

the empty cells show that there was no 4 wheeler with 5 cylinders, rear wheeler with 5 cylinders either, and finally zero cars where shown to have rear wheel drive and 4 cylinders.

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ .)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(. ~ cyl)
```

3. what does a "." do to the facet variables?
depending on where it is placed, it will affect weather the plot will be vertical or horizontal. it also seems to hide the function name and makes that variable void.

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)
```

4. the advantages of faceting data is that it is an easy way to get a quick visual to asses your data informally before moving forward. naturally because its a human behavior (visualizing) it is hard to scale up so it is not reliable with a large data set. when compared to color aesthetic, the more variables there are the more helpful color aesthetic would be because you can separate variables much more easily. 


5. Nrow is a command to nullify a row from the plot and Ncol is the command that nullifies a column/variable and fades it out but could potentially be given a colour that brightens it.



6. 


